Parsing Postfix log files

### 2008-08-07 doc/logparser-results.tex
Next step in the great renaming - renaming of graphs. In the process I removed some generated gnuplot input files from the repository.

\showgraph{build/plot-mails-received}{Number of mails received via SMTP per
day}{Mails received per day}

@@

\showgraph{build/plot-normal-filesize-numlines}{Parsing time, file size,
and number of lines}{parsing time vs file size vs number of lines graph}

\showgraph{build/plot-normal-filesize-numlines-factor}{Ratio of file size
and number of lines to parsing time}{parsing time vs file size vs number
lines factor}

@@

\showgraph{build/plot-normal-and-reverse-relative-to-shuffle}{Parsing time
relative to shuffled ordering}{Parsing time relative to shuffled ordering
graph}

@@

\showgraph{build/plot-full-ruleset-vs-minimum-ruleset}{Percentage parsing
time increase of maximum ruleset over minimum ruleset}{Percentage parsing
time increase of maximum ruleset over minimum ruleset}

@@

\showgraph{build/plot-cached-discarded-factor}{Increase in parsing time
when not caching compiled regexes}{Increase in parsing time when not
caching compiled regexes graph}

@@

\showgraph{build/plot-hits}{Hits per rule}{rule hits graph}

>>>>

\showgraph{build/graph-mails-received}{Number of mails received via SMTP per
day}{Mails received per day}

@@

\showgraph{build/graph-input-size-vs-parsing-time}{Parsing time, file size,
and number of lines}{parsing time vs file size vs number of lines graph}

\showgraph{build/graph-input-size-vs-parsing-time-ratio}{Ratio of file size
and number of lines to parsing time}{parsing time vs file size vs number
lines factor}

@@

\showgraph{build/graph-normal-and-reverse-vs-shuffle}{Parsing time relative
to shuffled ordering}{Parsing time relative to shuffled ordering graph}

@@

\showgraph{build/graph-full-ruleset-vs-minimum-ruleset}{Percentage parsing
time increase of maximum ruleset over minimum ruleset}{Percentage parsing
time increase of maximum ruleset over minimum ruleset}

@@

\showgraph{build/graph-cached-regexes-vs-discarded-regexes}{Increase in
parsing time when not caching compiled regexes}{Increase in parsing time
when not caching compiled regexes graph}

@@

\showgraph{build/graph-hits}{Hits per rule}{rule hits graph}
